---
title: "Markdown Demo"
author: "Tobin Magle"
date: "4/10/2018"
output: html_document
params:
          file:
                    label: "File"
                    value: ../data/complete_surveys.csv
                    input: file
                    
          sex:
            label: "Sex: "
            value: M
            input: select
            choices: [M, F]
            
          weight: 
                    label: "Weight"
                    value: 500
                    input: slider
                    max: 500
                    min: 0
---

```{r setup, include=FALSE}

library(tidyverse)
library(knitr)

surveys_complete<-read_csv(params$file)

surveys_complete<-surveys_complete%>%
          filter(sex==params$sex)%>%
          filter(weight<=params$weight)

```

#Small animal survey data

This is a survey of small animals from `r nlevels(as.factor(surveys_complete$plot_id))` plots
from the years `r min(surveys_complete$year)` to `r max(surveys_complete$year)`. Each row is an animal. 
Each column is an attribute of that animal. The variables recorded are `r names(surveys_complete)`.

#Sex table
Here is a breakdown of the number of female vs male animals observed in the study

```{r, table, echo = FALSE}
kable(surveys_complete%>%
                group_by(sex)%>%
                tally)
```

#Mean weight
The mean weight of all animals surveyed 
is `r mean(surveys_complete$weight, na.rm=TRUE)`.

#Relationship between hindfoot length and weight
We are interested in the relationship between weight and hindfoor length by species. Here is a graph.

```{r graph, echo=FALSE, fig.cap="Fig 1: Weight vs. hindfoot length"}
ggplot(data = surveys_complete, 
       aes(x = weight, 
           y = hindfoot_length, 
           color = species_id)) + 
          geom_point(alpha = 0.1,
           aes(color = species_id))
```